Synthesizing Quotient Lenses

### 2018-02-23 papers/QuotientLenses/main.tex
edits on 2

To begin, consider a bidirectional transformation that converts
\bibtex{} citation records such as
\begin{verbatim}
@Book {conway,
Author = "J. H. Conway",
Title = {Regular Algebra and Finite Machines}
}
\end{verbatim}
\noindent
into an equivalent EndNote format like the following
\begin{verbatim}
%0 Book
%T Regular Algebra and Finite Machines
%A J. H. Conway
%F conway
\end{verbatim}
\noindent
and vice versa.
%
Notice that transformations from one format to the other preserve
most of the information present in the data:  the title, the author,
and the key, for instance.  However, some information in the syntax
may be lost.  For instance, users are typically uninterested in preserving
the amount of the whitespace between words or
between fields.  The order of author and title fields is also likely
irrelevant and there may be equivalent ways of writing the same
name:  ``Conway, J. H.'' vs ``J. H. Conway.''

@@

\noindent
Indeed, Boomerang's quotient lenses are structured this way~\ref{boomerang}.
Of course, some of these elements are optional.  For instance, it is
not necessary to document internal and external formats.  However, we do
view it as good engineering practice to do so, as such documentation makes
lenses easier to read, understand, use and maintain.  In this case, there is
significant redundancy here:  External and internal formats
typically have some overlap; external formats and canonizers have related
structure; and the structure of bijective lens computations is largely driven
by the structure of the internal formats.  Hence, overall, a more compact
notation would simplify description and legibility of such computations.
In addition,
the lens and canonizer languages themselves can be somewhat fiddly and
difficult to
master.  For instance, to quotient out whitespace inside, and in between,
fields while also ignoring field order one must nest canonizing combinators
within one another in a somewhat tricky and fiddly way.

>>>>

To begin, consider a bidirectional transformation that converts
\bibtex{} citation records such as
\begin{verbatim}
@Book {conway,
Author = "J. H. Conway",
Title = {Regular Algebra and Finite Machines}
}
\end{verbatim}
\noindent
into an equivalent EndNote format like the following
\begin{verbatim}
%0 Book
%T Regular Algebra and Finite Machines
%A J. H. Conway
%F conway
\end{verbatim}
\noindent
and vice versa.
%
Notice that transformations from one format to the other preserve
most of the information present in the data:  the title, the author,
and the label, for instance.  However, some of the syntactic information
may be lost.  For instance, users are typically uninterested in preserving
whitespace between words or
between fields.  The order of author and title fields is also likely
irrelevant and there may be equivalent ways of writing the same
name:  ``Conway, J. H.'' vs ``J. H. Conway.''

@@

\noindent
Indeed, Boomerang's quotient lenses are structured this way~\ref{boomerang}.
Of course, some of these elements are optional.  For instance, it is
not necessary to document internal and external formats.  However, we do
view it as good engineering practice to do so, as such documentation makes
lenses easier to read, understand, use and maintain.  In this case, there is
significant redundancy here:  External and internal formats
typically have some overlap; external formats and canonizers have related
structure; and the structure of bijective lens computations is largely driven
by the structure of the internal formats.  Hence, overall, a more compact
notation would simplify description and legibility of such computations.
In addition,
the lens and canonizer languages themselves can be somewhat fiddly and
difficult to
master.  For instance, to quotient out whitespace inside, and in between,
fields while also ignoring field order, one must nest canonizing combinators
within one another in a somewhat tricky way.
